WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2021-01-01 method/sec_1-architectural_decisions.tex
Fixed comparison table

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Architecture Comparison with Existing Systems

\cref{fi:architecture_comparison} shows a comparison between existing systems and WDIAS concerning software architectural aspects. Here, we compare systems under categories such as data storage, performance, architecture, and other features. The \acrshort{fews} and \acrshort{msm} frameworks store the data on a central data service, which could become a bottleneck while handling large volumes of data in a critical situation. Other systems can use a pool of resources allowing them to increase the performance by adding more resources to the system. Regarding the performance of the systems, we consider scalability, availability, cloud computing support, and system deployment capabilities. All the systems can scale up to some extent by adding resources beforehand or in real-time. However, LEAD, DIAS, and WDIAS could scale on-demand by adding more resources and support automatic elasticity (i.e., scaling up and down). LEAD, MADIS, DIAS, and WDIAS have high availability, as they use a resource pool that can run on different locations. Further, these systems are capable of automatically handling partial system failures enabling fault tolerance. When we consider cloud computing support, the system should support easy integration with clouds. It is possible to rent virtual servers and deploy the local services in the cloud infrastructure, but some systems may not allow access to them remotely. Even though some systems can deploy in such a manner, they may not be capable of automatically allocating resources on demand. Hence, we cannot consider that those systems can utilize cloud infrastructures fully. Furthermore, we can easily maintain a system if it consists of independent subsystems, and each subsystem is capable of deploying or upgrading independently. Independent service deployment is a more flexible and better way to handle this, rather than copy-pasting codes to deploy changes.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.05\textwidth]{method/misc/architecture_comparison_pros_cons.pdf}
    \caption{Comparison of features among existing weather data assimilation and integration systems and \acrshort{wdias}. %An "X" in the table represents a feature offered by the corresponding tool. An "-" in the table represents that information available are not enough to make an statement, and empty presents a feature is not offered. 
    }
    \label{fi:architecture_comparison}
\end{figure}

We discuss the architecture of the systems in terms of their design, dependencies of the subsystems, extensibility, availability of source code, and data preprocessing capabilities specific to the weather domain. While other existing systems use distributed client-server architecture or monolithic distributed architecture, LEAD uses the SOA architecture. However, WDIAS has the advantage of using modern cloud computing technologies to implement microservices as containerized applications. The architecture implementation of independent subsystems allows users to maintain subsystems independently. Further, WDIAS enables different subsystems to be implemented using different technology stacks. Specially WDIAS and MSM provide an open-source framework that gives users the capability to enhance or modify the system as per the requirement. These systems provide data preprocessing capabilities for weather data and the ability to add new preprocessing capabilities. However, WDIAS is also capable of providing auto-scaling with data preprocessing. Workflow engine and model execution support are some other extra features that are helpful with weather forecasting. However, the WDIAS focuses on implementing a WDIA system with supporting main features, and it provides an extendable open framework to integrate such features easily.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Architecture Comparison with Existing Systems
\begin{table}[htp]
    \caption{Comparison of features among existing weather data assimilation and integration systems and \acrshort{wdias}. }
    \includegraphics[width=1.05\textwidth]{method/misc/architecture_comparison_pros_cons.pdf}
    \label{tab:architecture_comparison}
    {\raggedright \footnotesize An "\Cross" in the table represents a feature offered by the corresponding tool. An "\SmallHBar" in the table represents that information available are not enough to make an statement, and empty presents a feature is not offered. \par}
\end{table}

\cref{tab:architecture_comparison} shows a comparison between existing systems and WDIAS concerning software architectural aspects. Here, we compare systems under categories such as data storage, performance, architecture, and other features. The \acrshort{fews} and \acrshort{msm} frameworks store the data on a central data service, which could become a bottleneck while handling large volumes of data in a critical situation. Other systems can use a pool of resources allowing them to increase the performance by adding more resources to the system. Regarding the performance of the systems, we consider scalability, availability, cloud computing support, and system deployment capabilities. All the systems can scale up to some extent by adding resources beforehand or in real-time. However, LEAD, DIAS, and WDIAS could scale on-demand by adding more resources and support automatic elasticity (i.e., scaling up and down). LEAD, MADIS, DIAS, and WDIAS have high availability, as they use a resource pool that can run on different locations. Further, these systems are capable of automatically handling partial system failures enabling fault tolerance. When we consider cloud computing support, the system should support easy integration with clouds. It is possible to rent virtual servers and deploy the local services in the cloud infrastructure, but some systems may not allow access to them remotely. Even though some systems can deploy in such a manner, they may not be capable of automatically allocating resources on demand. Hence, we cannot consider that those systems can utilize cloud infrastructures fully. Furthermore, we can easily maintain a system if it consists of independent subsystems, and each subsystem is capable of deploying or upgrading independently. Independent service deployment is a more flexible and better way to handle this, rather than copy-pasting codes to deploy changes.

We discuss the architecture of the systems in terms of their design, dependencies of the subsystems, extensibility, availability of source code, and data preprocessing capabilities specific to the weather domain. While other existing systems use distributed client-server architecture or monolithic distributed architecture \cite{ChristensenBenDontMonolith}, LEAD uses the SOA architecture. However, WDIAS has the advantage of using modern cloud computing technologies to implement microservices as containerized applications. The architecture implementation of independent subsystems allows users to maintain subsystems independently. Further, WDIAS enables different subsystems to be implemented using different technology stacks. Specially WDIAS and MSM provide an open-source framework that gives users the capability to enhance or modify the system as per the requirement. These systems provide data preprocessing capabilities for weather data and the ability to add new preprocessing capabilities. However, WDIAS is also capable of providing auto-scaling with data preprocessing. Workflow engine and model execution support are some other extra features that are helpful with weather forecasting. However, the WDIAS focuses on implementing a WDIA system with supporting main features, and it provides an extendable open framework to integrate such features easily.

### 2021-01-01 summary/sec_1-conclusions.tex
Fix NWMs plural
Fixed comparison table

To enhance the accuracy of the weather forecast, we need to provide reliable and timely weather data for NWMs. Also, most of the existing weather data integration systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems. However, most of the concepts are outdated with the technology advancement, and we cannot get the full advantage of modern computational models such as containerized applications and using the cloud computing to gain benefits of scalability, high availability, and low-cost operations. Even though there are many weather data integration systems, most of them are proprietary or closed source. Thus, for an island like Sri Lanka that has different kinds of weather seasons yearly, those software needs to be highly customize.

@@

Compared to other existing weather data integration and assimilation systems, WDIAS has the advantage of taking full advantage of cloud computing technologies to implement a highly scalable and available system at low-cost. Because it uses containerized applications to implement the microservices, it allows independent service deployments. Each microservice can scale independently without affecting other microservices. Further, each microservice could use a suitable technology stack for the task. \acrshort{fews}, \acrshort{madis}, and \acrshort{msm} have platform dependencies, and some of the deployments are performed by copy-pasting source codes. The \acrshort{fews} and \acrshort{msm} provide a centralized data storage mechanism that  can become a bottleneck while processing a large volume of data in critical situations. \acrshort{madis} and \acrshort{dias} also support data storage arrays to store data. WDIAS and \acrshort{lead} can support a pool of resources based on the requirement.
Like other systems, WDIAS provides data preprocessing capabilities, and users can integrate new data preprocessing capabilities by implementing them as independent containerized microservice applications. Even though \acrshort{fews}, \acrshort{lead}, and \acrshort{msm} provide workflow engine support and model execution support, these can be achieved using an external workflow management system by fulfilling the data requirements via WDIAS. Further, WDIAS is an extendable open framework such that similar capabilities can be integrated as a new extension module system. Compared to other existing systems, the \acrshort{lead} is more scalable and is implemented using \acrshort{soa} architecture. However, with the help of modern container orchestration frameworks, such as Kubernetes and cloud computing technologies, those can provide high scalability and high availability as inherent capabilities. Those are mature enough to provide fault-tolerance automatically \cite{Scolati2019ADevices}. Implementing the deployment units as containerized applications based on the modern architecture patterns allows WDIAS to implement a highly scalable and high available system without heavy effort on those features.  A comparison  between WDIAS and other systems are presented in Table \ref{fi:architecture_comparison}.

>>>>

To enhance the accuracy of the weather forecast, we need to provide reliable and timely weather data for \acrshort{nwm}s. Also, most of the existing weather data integration systems are based on basic client-server architectures or monolithic distributed system architectures or developed based on the best technology available at the time of developing those systems. However, most of the concepts are outdated with the technology advancement, and we cannot get the full advantage of modern computational models such as containerized applications and using the cloud computing to gain benefits of scalability, high availability, and low-cost operations. Even though there are many weather data integration systems, most of them are proprietary or closed source. Thus, for an island like Sri Lanka that has different kinds of weather seasons yearly, those software needs to be highly customize.

@@

Compared to other existing weather data integration and assimilation systems, WDIAS has the advantage of taking full advantage of cloud computing technologies to implement a highly scalable and available system at low-cost. Because it uses containerized applications to implement the microservices, it allows independent service deployments. Each microservice can scale independently without affecting other microservices. Further, each microservice could use a suitable technology stack for the task. \acrshort{fews}, \acrshort{madis}, and \acrshort{msm} have platform dependencies, and some of the deployments are performed by copy-pasting source codes. The \acrshort{fews} and \acrshort{msm} provide a centralized data storage mechanism that  can become a bottleneck while processing a large volume of data in critical situations. \acrshort{madis} and \acrshort{dias} also support data storage arrays to store data. WDIAS and \acrshort{lead} can support a pool of resources based on the requirement.
Like other systems, WDIAS provides data preprocessing capabilities, and users can integrate new data preprocessing capabilities by implementing them as independent containerized microservice applications. Even though \acrshort{fews}, \acrshort{lead}, and \acrshort{msm} provide workflow engine support and model execution support, these can be achieved using an external workflow management system by fulfilling the data requirements via WDIAS. Further, WDIAS is an extendable open framework such that similar capabilities can be integrated as a new extension module system. Compared to other existing systems, the \acrshort{lead} is more scalable and is implemented using \acrshort{soa} architecture. However, with the help of modern container orchestration frameworks, such as Kubernetes and cloud computing technologies, those can provide high scalability and high availability as inherent capabilities. Those are mature enough to provide fault-tolerance automatically \cite{Scolati2019ADevices}. Implementing the deployment units as containerized applications based on the modern architecture patterns allows WDIAS to implement a highly scalable and high available system without heavy effort on those features.  A comparison  between WDIAS and other systems are presented in Table \ref{tab:architecture_comparison}.
